Methodology for Assessing the State of the Practice for Domain X

### 2021-10-20 StateOfPractice/Methodology/Methodology.tex
Further edits to the estimate of time section

    Domain analysis (with help of Domain Expert)
    (Section~\ref{SecDomainAnalysis}) & 25 \addtocounter{totHours}{20} \\

@@

	Gather source code and documentation for each package (20 minutes per
	package for 30 packages)) & 10 \addtocounter{totHours}{10} \\

@@

    Analyze data and answer research questions & 30 \addtocounter{totHours}{30}\\

@@

>>>>

    Domain analysis (with help of Domain Expert)
    (Section~\ref{SecDomainAnalysis}) & 20 \addtocounter{totHours}{20} \\

@@

	Gather source code and documentation for each package (10 minutes per
	package for 30 packages)) & 5 \addtocounter{totHours}{5} \\

@@

    Analyze data and answer research questions & 20 \addtocounter{totHours}{20}\\

@@

The total number of person hours is \total{totHours} hours.  This is close to
our goal of 1 month of person hours (160 hours).  The amount of time spent by
the Domain Expert can be estimated by summing the Domain Expert items in
Table~\ref{TabPersonHours} and adding an estimate of the time that they will
independently spend on their assigned tasks.  If we assume that the Domain
Expert will spend 2 hours on the domain analysis and another 2 hours with
answering questions, the Domain Expert time will be about 12 person hours.
